taxadb: A High-Performance Local Taxonomic Database Interface

### 2019-08-22 paper/manuscript.Rmd
minor unresolved names changes

Notice that one species name could not be resolved to a COL identifier.  This could indicate a data entry problem such as a misspelling of a name, but failure to resolve properly specified scientific names is not uncommon, as even large scale efforts like the Catalogue of Life are far from a comprehensive list of all published scientific names.

>>>>

Notice that one species name could not be resolved to a COL identifier.  This could indicate a data entry problem such as a misspelling of a name or the inclusion of a citation or year, which may be addressed by `clean_names()`. However, failure to resolve properly specified scientific names is not uncommon, as even large scale efforts like the Catalogue of Life are far from a comprehensive list of all published scientific names.
